Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/modeling.tex
--

%\subsection{Results \& Discussion}
\paragraph{Results and Discussion}
Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax scores for the images in the figure.
\gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material. All important points can be made at that level, and this way we gain space.}\sz{I would not do that}
% Apart from the evaluation on the full set of instances (column \textit{\mbox{All}} in Table~\ref{tab:model}), we further assess model effectiveness on the instances whose  \vg names do not match the top response in MN (\mbox{\textit{VG}$\neq$\textit{MN}}), and on those which were not part of the set of images used for training bottom-up (\mbox{$\neg$\textit{Training}}).
% The latter two sets are disjoint. 
Strikingly, the model performs worse on \vg than on the top MN response, even though the model was trained on \vg names and saw the majority of the instances during training: It has a general accuracy of $76.8$\ on MN, $68.7$\ on \vg (see condition \textit{All}), and in the subset where the top names differ (VG$\neq$MN) the difference is even bigger,\ $52.6$ vs.\ $20.7$.
We hypothesize two main reasons for this difference.
First, the top MN name may be more reliable because it is collected from multiple workers: For instance, in the rightmost example of the first row of Figure~\ref{fig:ex-high-low-agreement}, the VG annotator chose \textsl{sandwich}, but \textsl{hotdog} is more appropriate and accordingly it was chosen by most subjects in MN (note however that three workers still chose \textsl{sandwich}).
Second, the model can in some cases be subject to similar kinds of visual uncertainty as humans (cf.\ Section\ \ref{ssec:variation}), like mistaking a bridge for a street in the third image in the second row of Figure~\ref{fig:ex-high-low-agreement}.
% It achieves a higher accuracy of up to\ 55\% points on instances for which MN and the VG name differ (\textsc{buildings}, VG$\neq$MN). 
% The reasons may be that MN is more general than VG for many cases (e.g.,\ the examples for \textsl{batter} in Fig.\ \ref{fig:ex-high-low-agreement}), or that MN is more reliable due to up to $36$~annotations per instance as well as to our elicitation procedure\footnote{Recall that we instructed the workers explicitly to produce object names, and did not obtain them by canonicalizing object descriptions as was done for VG.} (e.g.,\ (\textsl{sandwich,hotdog}), Fig.\ \ref{fig:ex-high-low-agreement}).

@@

The dataset furthermore allows for comparing models on weighted naming alternatives, as illustrated by measuring the KL divergence. 
As shown in the table, the model outperforms the random baseline on all image sets. \cs{we could also (better?) use the average responses over all instances in MN -- TBD}
\gbt{The following is interesting but I would move it to supp. material (see above).}
It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Tab.\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}, which might \sz{?} contain occluded or unclear bounding boxes.% \cs{can we say that?}. 
%For these more difficult instances (VG$\neq$MN),for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain

Qualitative analysis suggests that Bottom-up presents many of the phenomena related to naming variation that we find in humans.
In some cases, the model does not make clear referential mistakes made by workers (e.g.,\ \textsl{boy-helmet},\ Fig.\ \ref{fig:ex-high-low-agreement}), but overall tends to mirror cases of human ``referential uncertainty'' 
(\textsl{man-shirt}, \textsl{bed-sheet}).
We also find cross-classification (\textsl{boy-batter}) and metonymy (\textsl{food-plate}). 
It also reflects perceptual mistakes caused by unclear images (\textit{street-bridge}), but makes also quite a few predictions which are unreasonable or inconsistent from a human perspective (and not contained in MN), such as \textsl{bridge-sky}, \textsl{player-dirt}. 
%
\iffalse
\begin{itemize}
	\item VG worse than MN; considering that model was trained on VG - is it because MN has easier labels? Does this mean that generalisation ability is better evaluated on MN?
	\item VG$\neq$MN much worse than All $\Rightarrow$ Former has more difficult/ambiguous images (for both? classifier and human?)
	\item for those more difficult images (VG$\neq$MN), the difference for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
	\item accuracy drops for notTrain (except for vehicles MN), but is still much better than VG$\neq$MN  
\end{itemize}

>>>>

%\subsection{Results \& Discussion}
\paragraph{Results and Discussion}
Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax scores for the images in the figure.
%\gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material. All important points can be made at that level, and this way we gain space.}\sz{I would not do that}
% Apart from the evaluation on the full set of instances (column \textit{\mbox{All}} in Table~\ref{tab:model}), we further assess model effectiveness on the instances whose  \vg names do not match the top response in MN (\mbox{\textit{VG}$\neq$\textit{MN}}), and on those which were not part of the set of images used for training bottom-up (\mbox{$\neg$\textit{Training}}).
% The latter two sets are disjoint. 
Strikingly, the model performs worse on \vg than on the top MN response, even though the model was trained on \vg names and saw the majority of the instances during training: It has a general accuracy of $76.8$\ on MN, $68.7$\ on \vg (see condition \textit{All}), and in the subset where the top names differ (VG$\neq$MN) the difference is even bigger,\ $52.6$ vs.\ $20.7$.
We hypothesize two main reasons for this difference.
First, the top MN name may be more reliable because it is collected from multiple workers: For instance, in the rightmost example of the first row of Figure~\ref{fig:ex-high-low-agreement}, the VG annotator chose \textsl{sandwich}, but \textsl{hotdog} is more appropriate and accordingly it was chosen by most subjects in MN (note however that three workers still chose \textsl{sandwich}).
Second, the model can in some cases be subject to similar kinds of visual uncertainty as humans (cf.\ Section\ \ref{ssec:variation}), like mistaking a bridge for a street in the third image in the second row of Figure~\ref{fig:ex-high-low-agreement}.
% It achieves a higher accuracy of up to\ 55\% points on instances for which MN and the VG name differ (\textsc{buildings}, VG$\neq$MN). 
% The reasons may be that MN is more general than VG for many cases (e.g.,\ the examples for \textsl{batter} in Fig.\ \ref{fig:ex-high-low-agreement}), or that MN is more reliable due to up to $36$~annotations per instance as well as to our elicitation procedure\footnote{Recall that we instructed the workers explicitly to produce object names, and did not obtain them by canonicalizing object descriptions as was done for VG.} (e.g.,\ (\textsl{sandwich,hotdog}), Fig.\ \ref{fig:ex-high-low-agreement}).

@@

The dataset furthermore allows for comparing models on weighted naming alternatives, as illustrated by measuring the KL divergence. 
As shown in the table, the model outperforms the random baseline on all image sets. \cs{we could also (better?) use the average responses over all instances in MN -- TBD}
\gbt{The following is interesting but I would move it to supp. material (see above).}
It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Tab.\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}.
%, which might \sz{?} contain occluded or unclear bounding boxes.% \cs{can we say that?}. 
%For these more difficult instances (VG$\neq$MN),for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain

Qualitative analysis suggests that Bottom-up presents many of the phenomena related to naming variation that we find in humans.
In some cases, the model does not make clear referential mistakes made by workers (e.g.,\ \textsl{boy-helmet},\ Fig.\ \ref{fig:ex-high-low-agreement}), but overall tends to mirror cases of human ``referential uncertainty'' 
(\textsl{man-shirt}, \textsl{bed-sheet}).
We also find cross-classification (\textsl{boy-batter}) and metonymy (\textsl{food-plate}). 
Finally, it reflects perceptual mistakes caused by unclear images (\textsl{street-bridge}), but makes also quite a few predictions which are unreasonable or inconsistent from a human perspective (and not contained in MN), such as \textsl{bridge-sky}, \textsl{player-dirt}. 
%
\iffalse
\begin{itemize}
	\item VG worse than MN; considering that model was trained on VG - is it because MN has easier labels? Does this mean that generalisation ability is better evaluated on MN?
	\item VG$\neq$MN much worse than All $\Rightarrow$ Former has more difficult/ambiguous images (for both? classifier and human?)
	\item for those more difficult images (VG$\neq$MN), the difference for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
	\item accuracy drops for notTrain (except for vehicles MN), but is still much better than VG$\neq$MN  
\end{itemize}
